---
title: "A multi-level analysis of data quality for formal software citation"
author: "David Schindler and Frank Krüger"
format: html
toc: false
code-line-numbers: true
editor: visual
execute: 
  warning: false
suppress-bibliography: true
---

# A multi-level analysis of data quality for formal software citation

1.  What types of resources are referenced by formal software citations?
2.  Is software formally cited without being mentioned in the full-text document?
3.  Do formal software references provide all necessary information to identify software, developer, and the used code base?
4.  How well are formal software references represented in scientific literature databases?

```{r}
library(tidyverse)
library(magrittr)
library(patchwork)
library(DescTools)
library(ggalluvial)
library(easyalluvial)
library(xtable)
library(rcompanion)

options(xtable.floating = FALSE)
options(xtable.timestamp = "")
options(warn=-1)
options(dplyr.summarise.inform = FALSE)

theme_set(theme_bw() +   
            theme(legend.position = 'top', 
                  strip.background = element_rect(fill="#E5E5E5"), 
                  plot.margin = unit(c(0,2,0,0), 'mm'),
                  legend.margin=margin(0,0,0,0),
                  legend.box.margin=margin(0,0,-5,0),
                  plot.caption.position = "plot",
                  plot.caption = element_text(hjust = 0),
                  plot.tag.position = "bottomleft")
)
```

## Citation Resource Types

The first analysis investigates the different types of resources that are referenced by formal software citations that appear in-text in the context of an informal software mention.

First up the required data is loaded. As outlined in the article, creation sentences are excluded for this analyses as they might add a bias.

```{r}
creation_articles <- read_csv('SoMeSci/Formal_Citation/creation_file_list.csv', 
                              show_col_types = F)
df_citation_types <- read_csv('SoMeSci/Formal_Citation/software_citation_type_annotation.csv', 
                              show_col_types = F) %>% 
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Book', 
    'Software_Article', 
    software_citation_type)) %>%
  mutate(paper = gsub(
    'https://www.ncbi.nlm.nih.gov/pmc/articles/', 
    '', 
    paper)) %>%
  select(-software) %>%
  distinct()
```

We look at the number of annotated references; filter for creation sentences; remove annotations that were found to not be software references; calculate multinomial confidence intervals for the relevant data.

```{r}
# Overall annotations
print(paste0("Number of annotations: ", nrow(df_citation_types)))

# Exclude Creation sentences 
df_citation_types %<>%
  filter(!paper %in% creation_articles$creation_file_list)
print(paste0(
  "Number of annotations without Creation Sentences: ", 
  nrow(df_citation_types)))

# Analyze and exclude irrelevant types
order <- c('Direct', 'Software_Article', 'Manual', 'Website', 'Other')
df_citation_types %>% 
  filter(!software_citation_type %in% order) %>%
  group_by(software_citation_type) %>%
  summarize(n=n()) %>%
  print(.)

df_citation_types %<>% 
  filter(software_citation_type %in% order) 
print(paste0("Number of relevant annotations: ", nrow(df_citation_types)))  

# Calculate CIs
df_citation_types %>%
  group_by(software_citation_type) %>%
  summarize(n=n()) -> df_tmp
df_tmp_2 <- data.frame(MultinomCI(df_tmp$n, conf.level = 0.95))
df <- bind_cols(df_tmp, df_tmp_2)

print(mutate(df, across(3:5, round, 3)))

```

Plotting the results:

```{r}

df %>%
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Software_Article', 
    'Article', 
    software_citation_type)) %>%
  mutate(software_citation_type = factor(
    software_citation_type, 
    levels=c('Direct', 'Article', 'Manual', 'Website', 'Other'))) %>%
  ggplot(aes(software_citation_type, est)) + 
  geom_point() + 
  geom_errorbar(aes(ymin=lwr.ci, ymax=upr.ci), width=.5)+
  labs(x="Citation Type", y = "Relative Amount") +
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6),
                     labels = c("0%", "20%", "40%", "60%")) +
  facet_wrap(~ "Distribution of Citation Types", nrow=2, scales='free_y') -> 
  p_out

ggsave('citation_type_amounts.jpg', p_out, width = 8, height = 2.5)

p_out <- p_out + labs(x="Citation Type", y = "Relative Amount",
       caption="Fig S1 (Article Fig 3): Relative amount of different 
       software citation types with confidence intervals.")
print(p_out)

```

Looking at the interaction between resource type and provided meta-data in the informal mention. This allows to determine if authors provide additional meta-data missing from formal references in the articles full-text document.

```{r}
# Reloading the annotation data because we need the exact software mention 
# string that was removed as duplicates before
df_citation_types <- read_csv('SoMeSci/Formal_Citation/software_citation_type_annotation.csv') %>% 
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Book', 
    'Software_Article', 
    software_citation_type)) %>%
  mutate(paper = gsub(
    'https://www.ncbi.nlm.nih.gov/pmc/articles/', 
    '', 
    paper)) %>%
  distinct() %>%
  filter(!paper %in% creation_articles$creation_file_list) %>% 
  filter(software_citation_type %in% order) 

# Loading original SoMeSci data
df_software <- read_csv('SoMeSci/Formal_Citation/software_sparql.csv')

# Matching the dataframes
df_software %>%
  mutate(article = gsub('http://data.gesis.org/somesci/', '', article)) %>%
  select(sw_identity, spelling, article, cit_string) %>%
  distinct() %>%
  right_join(
    df_citation_types, 
    by=c('article'='paper', 'spelling'='software', 'cit_string'='citation')) %>%
  select(-c(spelling, cit_string, citation_index)) -> 
  df_citations 

# Transforming results and calculating binomial CIs
# Website and Other are not included because there are to few samples
df_software %>%
  mutate(
    ver_string = ifelse(is.na(ver_string), FALSE, TRUE), 
    cit_string = ifelse(is.na(cit_string), FALSE, TRUE), 
    dev_string = ifelse(is.na(dev_string), FALSE, TRUE), 
    rel_string = ifelse(is.na(rel_string), FALSE, TRUE), 
    url_string = ifelse(is.na(url_string), FALSE, TRUE),
    ext_string = ifelse(is.na(ext_string), FALSE, TRUE),
    abb_string = ifelse(is.na(abb_string), FALSE, TRUE),
    alt_string = ifelse(is.na(alt_string), FALSE, TRUE)
  ) %>% 
  mutate(
    ver_string = ifelse(ver_string | rel_string, TRUE, FALSE), 
    alt_string = ifelse(abb_string | alt_string, TRUE, FALSE)) %>%
  select(-c(spelling, lic_string, abb_string, rel_string)) %>%
  group_by(sw_identity, article) %>%
  summarize(
    ver_string = any(ver_string),
    dev_string = any(dev_string),
    cit_string = any(cit_string),
    url_string = any(url_string),
    ext_string = any(ext_string),
    alt_string = any(alt_string)
    , .groups='drop') %>%
  mutate(article = gsub('http://data.gesis.org/somesci/', '', article)) %>%
  left_join(df_citations, by=c('sw_identity', 'article')) %>% 
  mutate(
    software_citation_type=ifelse(
      is.na(software_citation_type), 
      'None', 
      software_citation_type)) -> df_tmp #%>%

df_tmp %>% 
  filter(software_citation_type %in% c('None', 'Software_Article')) %>%
  mutate(software_citation_type = ifelse(software_citation_type == 'None', 1, 0)) %>%
  mutate(ver_string = ifelse(ver_string, 1, 0)) -> df_test

# Performing a Chi-sq test to evaluate if the probability for providing a 
# software mention in the article full-text document differs between 
# software cited with a software articles and software not cited at all. 
# And assessing the extent of the effect.  
nrow(df_test)
chisq.test(df_test$software_citation_type, df_test$ver_string)
cramerV(df_test$software_citation_type, df_test$ver_string)
cohenW(df_test$software_citation_type, df_test$ver_string)

df_tmp %>%
  group_by(software_citation_type) %>%
  mutate(n_software = n()) %>%
  group_by(software_citation_type, n_software) %>%
  summarize(across(3:8, sum)) %>%
  pivot_longer(!c(software_citation_type, n_software)) %>%
  mutate(rel=value / n_software) %>%
  mutate(MoE = sqrt((rel * (1-rel))/n_software) * 1.96) %>%
  mutate(CIl = rel-MoE, CIu = rel + MoE) %>%
  mutate(rel=rel*100, CIu=CIu*100, CIl=CIl*100) %>%
  mutate(CIu = pmin(CIu, 100), CIl = pmax(CIl, 0)) %>%
  filter(!name %in% c('cit_string', 'ext_string')) %>%
  ungroup() %>%
  mutate(name=recode(name, 
                     ver_string='Version', 
                     dev_string='Developer', 
                     url_string='URL', 
                     alt_string='Alternative Name', 
                     ext_string='Extension')) %>%
  mutate(name=factor(name, level=c('Version', 
                                   'Developer', 
                                   'URL', 
                                   'Alternative Name', 
                                   'Extension'))) %>%
  mutate(software_citation_type=factor(
    software_citation_type, 
    level=c('None', 'Software_Article', 'Direct', 
            'Manual', 'Website', 'Other'))) %>%
  filter(! software_citation_type %in% c('Website', 'Other')) %>%
  print(., n=16) -> df_plot

# Plotting the results
df_plot %>%
  ggplot(., aes(software_citation_type,rel, color=name)) +
  geom_point(position=position_dodge(width=.7)) +
  geom_errorbar(aes(ymin=CIl, ymax=CIu), 
                width=.5, position=position_dodge(width=.7)) +
  labs(x='Information',
       y='Rel. Number of Mentions (%)') +
  scale_color_manual('Software', values=c('#bee383', '#fdcb97', '#bdc9e1', '#e0c2cd')) -> 
  p_out

ggsave('completeness_with_informal.jpg', p_out, width = 8, height = 2.5)

p_out <- p_out + labs(caption="Fig S2 (Article Fig 4): Relative amount of meta-data 
       provided with respect to the formal citation type. Software 
       mentions that were not formally cited are aggregated under 
       label ''None''. 95% CIs are shown.")
print(p_out)
```

## Formal Software Citation without in-text Software Mention

All references were annotated in order to identify instances of direct software citations, manual citations, and software website citations that are not connected to an in-text software mention. Here, the amount of relevant cases is counted and set in context to the number of samples with in-text software mentions to determine how often this is actually the case in practice.

First, the data is loaded. Since the references were only annotated for PLoS methods and PubMed full-texts of the [SoMeSci](https://data.gesis.org/somesci/) data set, the remaining resource type annotations are excluded.

```{r}
df_new_citation_types <- read_csv('SoMeSci/Formal_Citation/software_citation_type_annotation_without_intext_mention.csv', 
                                  show_col_types = F) %>%
  select(-software)
df_plos_and_pubmed <- read_csv('SoMeSci/Formal_Citation/fulltext_and_methods_list.csv', 
                               show_col_types = F)
df_citation_types <- read_csv('SoMeSci/Formal_Citation/software_citation_type_annotation.csv', 
                              show_col_types = F) %>% 
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Book', 
    'Software_Article', 
    software_citation_type)) %>%
  mutate(paper = gsub('https://www.ncbi.nlm.nih.gov/pmc/articles/', 
                      '', 
                      paper)) %>%
  select(-software) %>%
  distinct() %>%
  filter(paper %in% df_plos_and_pubmed$list) %>% 
  filter(software_citation_type %in% c('Direct', 'Manual', 'Website')) 
```

Determining the amount of newly identified references:

```{r}
df_new_citation_types %>%
  group_by(software_citation_type, outside) %>%
  summarize(n_citations=n(), n_articles=n_distinct(paper)) %>% print(.)

df_new_citation_types %>%
  filter(!outside) %>%
  group_by(reason) %>%
  summarize(n=n()) %>% print(.)

df_new_citation_types %>%
  filter(!outside) %>%
  filter(!reason %in% c('error', 'somesci error')) %>%
  group_by(software_citation_type) %>%
  summarize(n_new_citations=n(), n_new_articles=n_distinct(paper)) %>% 
  print(.) -> 
  df_tmp

df_citation_types %>% 
  group_by(software_citation_type) %>%
  summarize(n_citations=n(), n_articles=n_distinct(paper)) %>%
  inner_join(df_tmp, by='software_citation_type') %>%
  mutate(rel = n_new_citations / (n_new_citations + n_citations))
```

## Citation Completeness

In the next analyses step the completeness of formal references is analyzed. For this purpose, meta-data contained in formal references was systematically annotated. The data is analyzed in three steps: 1. the amount of provided meta-data is analyzed directly, 2. the provided meta-data is analyzed in terms of software identification, author attribution, and code base identification, and 3. the meta-data is analyzed in combination with meta-data from informal in-text software mentions.

```{r}
# Aggregated data on completeness from the annotation
df_txt <- read_csv("SoMeSci/Formal_Citation/info_summary_txt.csv", 
                   show_col_types = F) %>%
  filter(!File %in% creation_articles$creation_file_list) 

# File required for mapping annotations to original SoMeSci annotation
df_map <- read_csv("SoMeSci/Formal_Citation/original_data_matching.csv", 
                   show_col_types = F) %>% 
  mutate(article = gsub('https://www.ncbi.nlm.nih.gov/pmc/articles/', '', article))

df_txt %<>%
  left_join(df_map, by=c('File'='article', 'Idx'='citation_id')) %>%
  left_join(df_new_citation_types, by=c('File'='paper', 'Idx'='citation')) %>%
  mutate(software_citation_type = ifelse(
    is.na(cite_type), 
    software_citation_type, 
    cite_type)) %>%
  select(-c(cite_type, outside, reason)) 
```

1.  Amount of provided meta-data

```{r}
order <- c('Name', 'Identifier', 'Archive', 'URL', 'Creator', 'Version', 
           'PubDate_exact', 'PubDate_year', 'Date_of_access', 
           'Description', 'Type_of_citation')
print(paste0(nrow(df_txt), " references were analyzed for completeness"))

df_txt %>%
  rename(Identifier=ID) %>%
  select(-software) %>%
  distinct() %>%
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Manual', 
    'Manual', 
    'Direct')) %>%
  group_by(software_citation_type) %>%
  mutate(n=n()) %>%
  group_by(software_citation_type, n) %>%
  summarize(across(Creator:License, sum)) %>%
  pivot_longer(cols=!c(software_citation_type, n), 
               names_to = "info", 
               values_to = "c") %>%
  mutate(rel = c/n) %>%
  mutate(MoE = sqrt((rel * (1-rel))/n) * 1.96) %>%
  mutate(CIu = rel + MoE, CIl = rel-MoE)  %>%
  mutate(rel = rel*100, CIu=pmin(100, CIu*100), CIl=pmax(0, CIl*100)) %>%
  filter(info %in% order) %>% 
  mutate(info=factor(info, levels = order)) %>%
  mutate(info = recode(info, 
                       `PubDate_year`='Year', 
                       `PubDate_exact`='Date', 
                       `Date_of_access`='Access', 
                       `Type_of_citation`='Type')) %>% 
  print(., n=22) %>%
  ggplot(aes(info, rel, color=software_citation_type)) + 
  geom_point(position=position_dodge(width=.7)) + 
  geom_errorbar(aes(ymin=CIl, ymax=CIu), 
                width=.6, 
                position=position_dodge(width=.7)) +
  labs(x="Meta-data", y = "Relative Amount") +
  scale_color_manual(values=c('#a6bae1', '#bee383')) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100),
                     labels = c("0%", "20%", "40%", "60%", "80%", "100%")) +
  guides(color = guide_legend(nrow=1, title="Citation Type")) +
  facet_wrap(~ "Amount of provided meta-data") -> p_out

ggsave('completeness_info.jpg', p_out, width = 8, height = 2.5)

p_out <- p_out + labs(caption="Fig S3 (Article Fig 5): Relative citation completeness with 95% CIs.")
print(p_out)
```

2.  Identification, attribution, code base

```{r}
order = c('identifiable_creator', 
          'identifiable_id', 
          'identifiable_archive', 
          'identifiable_precise',
          'identifiable_url',
          'identifiable_imprecise',
          'creator_attribution',
          'codebase_version',
          'codebase_release',
          'codebase_precise',
          'codebase_doa',
          'codebase_imprecise')

order_n = c('creator', 
          'id', 
          'archive',
          'version', 
          'release',
          'precise',
          'url',
          'doa',
          'imprecise',
          'attribution')

# Identifiability of software
df_txt %>%
  mutate(identifiable_creator=Name & Creator) %>%
  mutate(identifiable_id=ID) %>%
  mutate(identifiable_archive=Archive) %>%
  mutate(identifiable_precise=identifiable_creator | 
           identifiable_id | 
           identifiable_archive) %>%
  mutate(identifiable_url=URL) %>%
  mutate(identifiable_imprecise=identifiable_precise | identifiable_url) -> 
  df_tmp

# Creator attribution
df_tmp %<>%
  mutate(creator_attribution=identifiable_creator) 

# Code base identification
df_tmp %<>% 
  mutate(codebase_release=PubDate_exact & identifiable_imprecise) %>% 
  mutate(codebase_version=Version & identifiable_imprecise) %>%
  mutate(codebase_precise=codebase_release | codebase_version) %>%
  mutate(codebase_doa=Date_of_access & identifiable_imprecise) %>%
  mutate(codebase_imprecise=codebase_precise | codebase_doa) 

# Plotting
df_tmp %>%
  select(-c(software, Creator, Name, Archive, PubDate_year, PubDate_exact, 
            PubDate_nd, ID, URL, Version, Date_of_access, Type_of_citation, 
            Description, License)) %>%
  distinct() %>%
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Manual', 
    'Manual', 
    'Direct')) %>%
  group_by(software_citation_type) %>%
  mutate(n=n()) %>%
  group_by(software_citation_type, n) %>%
  summarize(across(identifiable_creator:codebase_imprecise, sum)) %>%
  pivot_longer(cols=!c(software_citation_type, n), 
               names_to = "info", 
               values_to = "c") %>%
  mutate(rel = c/n) %>%
  mutate(MoE = sqrt((rel * (1-rel))/n) * 1.96) %>%
  mutate(CIu = rel + MoE, CIl = rel-MoE)  %>%
  mutate(rel = rel*100, CIu=pmin(CIu*100, 100), CIl=pmax(CIl*100,0)) %>%
  mutate(info = factor(info, levels = order)) %>% 
  separate(info, sep='_', into=c('Problem', 'quality')) %>%
  mutate(quality = factor(quality, levels=order_n)) %>%
  mutate(Problem = factor(Problem, levels=c('identifiable', 
                                            'creator', 
                                            'codebase'))) %>%
  print(., n=24) %>%
  ggplot(aes(quality, rel, color=software_citation_type)) + 
  geom_point(position=position_dodge(width=.7)) + 
  geom_errorbar(aes(ymin=CIl, ymax=CIu), 
                width=.6, 
                position=position_dodge(width=.7)) +
  labs(x="Identifiability", y = "Relative Amount") +
  scale_color_manual(values=c('#a6bae1', '#bee383')) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100),
                     labels = c("0%", "20%", "40%", "60%", "80%", "100%")) +
  guides(color = guide_legend(nrow=1, title="Citation Type")) +
  facet_grid(~Problem, scales = "free_x", space='free_x') -> p_out

ggsave('completeness_identification.jpg', p_out, width = 8, height = 2.5)

p_out <- p_out + labs(caption="Fig S4 (Article Fig 6): Relative citation completeness 
       with confidence intervals. Regarding software identification, 
       ''precise'' describes cases in which software is clearly 
       identifiable, while ''imprecise'' includes cases where only a URL 
       is provided as identifier, which is considered as unsuited to 
       clearly identify a software with details outlined in the article.
       Regarding codebase identification, the categories are defined 
       similarly, with ''imprecise'' including cases where only a 
       Date of Access is provided.")
print(p_out)
```

3.  Informal and formal meta-data

This step aggregates over formally and informally provided meta-data in order to determine the overall completeness. Therefore, this step is only performed for samples that have in-text software mentions and excluding the additional samples identified in the previous step.

```{r}
# Mapping all software names 
df_software %>%
  select(sw_identity, spelling) %>%
  distinct() -> df_spell_map

# Transforming the original SoMeSci information
df_software %>%
  mutate(
    ver_string = ifelse(is.na(ver_string), FALSE, TRUE), 
    dev_string = ifelse(is.na(dev_string), FALSE, TRUE), 
    rel_string = ifelse(is.na(rel_string), FALSE, TRUE), 
    url_string = ifelse(is.na(url_string), FALSE, TRUE),
    ext_string = ifelse(is.na(ext_string), FALSE, TRUE),
    abb_string = ifelse(is.na(abb_string), FALSE, TRUE),
    alt_string = ifelse(is.na(alt_string), FALSE, TRUE),
    cit_string = ifelse(is.na(cit_string), '', cit_string)
  ) %>% 
  mutate(ver_string = ifelse(
    ver_string | rel_string, TRUE, FALSE), 
    alt_string = ifelse(abb_string | alt_string, TRUE, FALSE)) %>%
  select(-c(spelling, lic_string, abb_string, rel_string)) %>%
  group_by(sw_identity, article) %>%
  summarize(
    ver_string = any(ver_string),
    dev_string = any(dev_string),
    url_string = any(url_string),
    ext_string = any(ext_string),
    alt_string = any(alt_string),
    cit_string = max(cit_string)
    , .groups='drop') %>%
  mutate(article = gsub('http://data.gesis.org/somesci/', '', article)) %>%
  filter(cit_string != "") %>%
  distinct() -> df_tmp

df_txt %>%
  select(-c(Name, Archive, PubDate_year, PubDate_exact, PubDate_nd, ID, 
            Date_of_access, Type_of_citation, Description, License)) %>%
  inner_join(df_spell_map, by=c('software'='spelling')) %>%
  inner_join(df_tmp, by=c('File'='article', 
                          'original_cite'='cit_string', 
                          'sw_identity'='sw_identity')) %>% 
  select(-c(alt_string, ext_string, software, sw_identity)) %>%
  distinct() %>%
  select(-c(Manual, original_cite, cite_idx)) %>%
  mutate(software_citation_type = ifelse(
    software_citation_type == 'Manual', 
    'Manual', 
    'Direct')) %>%
  group_by(software_citation_type) %>%
  mutate(n=n()) %>%
  rename(Version_informal=ver_string, 
         Developer_informal=dev_string, 
         URL_informal=url_string) %>%
  rename(Version_formal=Version, 
         Developer_formal=Creator, 
         URL_formal=URL) %>%
  mutate(Version_overall = Version_formal | Version_informal, 
         Developer_overall = Developer_formal | Developer_informal, 
         URL_overall = URL_formal | URL_informal) %>%
  group_by(software_citation_type, n) %>%
  summarize(across(!c(File, Idx), sum)) %>%
  pivot_longer(cols=!c(software_citation_type, n), 
               names_to = "info", 
               values_to = "c") %>%
  mutate(rel = c/n) %>%
  mutate(MoE = sqrt((rel * (1-rel))/n) * 1.96) %>%
  mutate(CIu = rel + MoE, CIl = rel-MoE)  %>%
  mutate(rel = rel*100, CIu=CIu*100, CIl=pmax(0, CIl*100)) %>% 
  mutate(CIu = pmin(CIu, 100), CIl = pmax(CIl, 0)) %>%
  separate(info, into = c('Metadata', 'Citation Type')) %>%
  mutate(Metadata=factor(Metadata, 
                         level=c('Developer', 'Version', 'URL'))) %>% 
  select(-c(c, n)) %>%
  print(.) %>%
  ggplot(aes(Metadata, rel, color=`Citation Type`)) + 
  geom_point(position=position_dodge(width=.5)) +
  geom_errorbar(aes(ymin=CIl, ymax=CIu), 
                width=.4, 
                position=position_dodge(width=.5)) +
  labs(x='Information',
       y='Relative Number of Mentions (%)',
       caption="Figure S5: Relative citation completeness for direct citation and 
       manual citation with respect to developer, version, and URL, considering 
       formally provided, informally provided information, and their combination.") +
  scale_color_manual(values=c('#a1dab4', '#41b6c4', '#225ea8')) +
  facet_wrap(~software_citation_type) -> p_out

print(p_out)

ggsave('completeness_metadata_with_informal.jpg', p_out, width = 8, height = 2.5)
```

## Database Representation

The database representation of formal software citations, manuals, and software websites was systematically annotated for the publisher's JATS XML representation, and the Semantic Scholar and Crossref entries. Aside from annotation if specific information is available it was also annotated if the information is structured, and whether it is correct. The corresponding references are analyzed by directly comparing their representation between the three sources.

First, the required data is loaded. This is more complex as before as separate data for each representation is loaded and then matched together. Moreover, here it is not filtered for arrticles from the SoMeSci Creation sentences because they do not add a bias as we are only interested in how well they entries are represented and we can increase the sample size by adding them.

```{r}
# Loading required functions for plotting and output, 
# that are too long for this file. 
source("plot_function.R")

# Aggregated data on completeness from the annotation
df_txt <- read_csv("SoMeSci/Formal_Citation/info_summary_txt.csv", 
                   show_col_types = F) %>%
  mutate(source = "TXT") %>%
  left_join(df_map, by=c('File'='article', 'Idx'='citation_id')) %>%
  left_join(df_new_citation_types, by=c('File'='paper',
                                        'Idx'='citation')) %>%
  mutate(software_citation_type = ifelse(
    is.na(cite_type),
    software_citation_type, 
    cite_type)) %>%
  select(-c(cite_type, outside, reason, software)) %>% 
  distinct()

df_txt %>%
  select(File, Idx, software_citation_type) -> df_tmp

df_xml <- read_csv("SoMeSci/Formal_Citation/info_summary_xml.csv", 
                   show_col_types = F) %>%
  inner_join(df_tmp, by=c('File', 'Idx')) %>%
  mutate(source="XML")

df_sem <- read_csv("SoMeSci/Formal_Citation/info_summary_sem.csv", 
                   show_col_types = F) %>%
  inner_join(df_tmp, by=c('File', 'Idx')) %>%
  mutate(source='SEM')

df_cro <- read_csv("SoMeSci/Formal_Citation/info_summary_cro.csv", 
                   show_col_types = F) %>%
  inner_join(df_tmp, by=c('File', 'Idx')) %>%
  mutate(source="CRO")

list(df_txt, df_xml, df_sem, df_cro) %>%
  bind_rows() ->
  df

df %<>%
  mutate(missing = ifelse(reference_missing, 
                          "reference_missing", 
                          ifelse(article_missing, 
                                 "article_missing",
                                 "covered"))) 

# Software article database availability annotation
df_software_article <- read_csv("SoMeSci/Formal_Citation/software_article_reference_availability.csv", 
                                show_col_types = F) 

```

Looking for duplicate entries that are sometimes present in databases, especially for Semantic Scholar. In case duplicate entries do exist, the one covering the most information is selected for subsequent analyses, where information is weighted

```{r}
# Looking at entries
df %>% 
  group_by(source, software_citation_type, File, Idx) %>% 
  summarize(n=n()) %>% 
  arrange(desc(n)) %>%
  group_by(source, software_citation_type, n) %>% 
  summarize(count = n()) %>% 
  filter(n > 1) %>% print(.) -> df_tmp
print(sum(df_tmp$count))

df %>%
  select(File, Idx, software_citation_type, reference_missing, article_missing, source) %>%
  filter(source == 'SEM') %>%
  distinct() %>%
  filter(!(reference_missing | article_missing)) %>% 
  group_by(software_citation_type) %>% 
  summarize(n = n())

# Removing duplicate entries 
df %<>%
  mutate(source = factor(source, levels=c("TXT", "XML", "CRO", "SEM"))) %>%
  mutate(completeness_count=Creator*2 + Name*4 + Archive*4 + ID*4 + URL*2 + 
           PubDate_exact*2 + PubDate_year + Version*2 + Type_of_citation * 0.5 + 
           Description * 0.5 + Date_of_access) %>%
  group_by(source, File, Idx) %>%
  slice_max(order_by=completeness_count, with_ties=F) %>%
  ungroup() %>%
  select(-completeness_count)
```

Next, we analyze the number of cases where wrong information is introduced by a database that does not stand in relation to the original information provided in the formal citation.

```{r}
# Number of wrong information added
df %>% 
  filter(source %in% c('CRO', 'SEM')) %>%
  filter(!(reference_missing | article_missing)) %>%
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Website', 'Other'), 
    'Direct', 
    software_citation_type)) %>%
  group_by(source, software_citation_type) %>% 
  mutate(n_total=n()) %>% 
  filter(wrong_content > 0) %>%
  select(source, software_citation_type, n_total, File, Idx, wrong_content) %>%
  group_by(source, software_citation_type, n_total) %>%
  summarize(n_references=n()) %>% 
  mutate(rel_references = n_references / n_total) %>%
  mutate(MoE = sqrt((rel_references * (1-rel_references))/n_total) * 1.96) %>%
  mutate(CIu = rel_references + MoE, CIl = rel_references-MoE)  %>%
  mutate(rel_references = rel_references*100, 
         CIu=CIu*100, 
         CIl=pmax(0, CIl*100)) %>% 
  mutate(CIu = pmin(CIu, 100), CIl = pmax(CIl, 0)) 

# Number of duplicate information added
df %>%
  filter(!(reference_missing | article_missing)) %>%
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Website', 'Other'), 
    'Direct', 
    software_citation_type)) %>%
  group_by(source, software_citation_type) %>% 
  mutate(n_total=n()) %>% 
  filter(duplicate > 0) %>%
  select(source, software_citation_type, n_total, File, Idx, duplicate) %>%
  group_by(source, software_citation_type, n_total) %>%
  summarize(n_references=n()) %>% 
  mutate(rel_references = n_references / n_total) %>%
  mutate(MoE = sqrt((rel_references * (1-rel_references))/n_total) * 1.96) %>%
  mutate(CIu = rel_references + MoE, CIl = rel_references-MoE)  %>%
  mutate(rel_references = rel_references*100, 
         CIu=CIu*100, 
         CIl=pmax(0, CIl*100)) %>% 
  mutate(CIu = pmin(CIu, 100), CIl = pmax(CIl, 0)) 

# Overlap between wrong and duplicate
df %>% 
  filter(wrong_content > 0 & duplicate > 0) %>%
  select(source, software_citation_type, File, Idx, wrong_content, duplicate)

```

Assessing the number of missing references in order to determine if software references are systematically missing from a database.

```{r}
df_software_article %>%
  pivot_longer(c(cro_status, sem_status), 
               names_to = 'source', 
               values_to = 'missing') %>%
  mutate(source = ifelse(source == 'sem_status', 'SEM', 'CRO')) %>%
  mutate(software_citation_type = 'Article') %>%
  rename(File=paper, Idx=citation) -> df_tmp

df %>%
  select(File, Idx, source, missing, software_citation_type) %>%
  filter(source %in% c('CRO', 'SEM')) -> df_tmp_2

df_tmp <- bind_rows(df_tmp, df_tmp_2)
df_tmp %>%
  filter(missing != 'article_missing') %>% 
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Website', 'Other'), 
    'Direct', 
    software_citation_type)) %>%
  group_by(software_citation_type, source) %>%
  mutate(n_total=n()) %>%
  group_by(software_citation_type, source, missing, n_total) %>%
  summarize(n=n()) %>%
  mutate(rel = n / n_total) %>% 
  mutate(MoE = sqrt((rel * (1-rel))/n_total) * 1.96) %>%
  mutate(CIu = rel + MoE, CIl = rel-MoE)  %>%
  mutate(rel = rel*100, CIu=CIu*100, CIl=pmax(0, CIl*100)) %>% 
  mutate(CIu = pmin(CIu, 100), CIl = pmax(CIl, 0)) #%>%
  #filter(missing == 'reference_missing')

df_tmp %>%
  filter(missing != 'article_missing') %>% 
  filter(source == 'SEM') %>%
  filter(software_citation_type != 'Manual') %>%
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Direct', 'Manual', 'Website', 'Other'), 
    1, 
    0)) %>%
  mutate(missing = ifelse(missing == 'covered', 1, 0)) -> df_test

# Performing a Chi-sq test to assess if direct software citations and 
# software articles (represented as regular articles) are missing with 
# different frequency from Semantic Scholar, to analyze if there is a 
# systematic bias. And asssesing the extend of the effect. 
nrow(df_test)
chisq.test(df_test$missing, df_test$software_citation_type)
cramerV(df_test$missing, df_test$software_citation_type)
cohenW(df_test$missing, df_test$software_citation_type)

df_tmp %>%
  filter(missing != 'article_missing') %>% 
  filter(source == 'CRO') %>%
  filter(software_citation_type != 'Manual') %>%
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Direct', 'Manual', 'Website', 'Other'), 
    1, 
    0)) %>%
  mutate(missing = ifelse(missing == 'covered', 1, 0)) -> df_test

# Performing a Chi-sq test to assess if direct software citations and 
# software articles (represented as regular articles) are missing with 
# different frequency from Crossref, to analyze if there is a 
# systematic bias. And asssesing the extend of the effect.
nrow(df_test)
chisq.test(df_test$missing, df_test$software_citation_type)
cramerV(df_test$missing, df_test$software_citation_type)
cohenW(df_test$missing, df_test$software_citation_type)
```

Now, the availability, structure, and correctness of representation is investigated for all provided information individually.

First, the representation with respect to version numbers is analyzed.

```{r}
# Setting up helper function and coloring scheme
drei <- function(available, attribute, string='S', missing=F){
  factor(
    ifelse(missing, "M", 
           ifelse(!available, "NA", 
                  ifelse(attribute, "US", string))))
}
vier <- function(missing, attribute, wrong, incomplete, place){
  factor(
    ifelse(missing, 'M', 
           ifelse(!attribute, 'NA', 
                  ifelse(wrong, 'E', 
                         ifelse(incomplete, 'E', 
                                ifelse(place, 'E', 'C'))))))
}
col_vector = c('#e0c2cd', '#a6bae1', '#fdcb97', '#bee383', '#e5d8bd', '#fcbbbb')
col_vector_flow = c('#a6bae1', '#fdcb97', '#bee383')

# Transformations for all following analyses
df %<>%
  mutate(software_citation_type = ifelse(
    software_citation_type %in% c('Website', 'Other'),
    'Direct', 
    software_citation_type)) %>%
  mutate(missing = ifelse(missing == 'covered', F, T)) %>%
  mutate(source = fct_recode(source, "JATS"="XML")) %>%
  mutate(source = factor(source, levels=c("JATS", "CRO", "SEM"))) %>%
  filter(source!="TXT") %>%
  mutate(id=paste0(File,Idx))

create_alluvial <- function(df, col_v1, col_vf1, col_v2, col_vf2, labels, title){
  df %>%
    filter(source == 'JATS') %>%
    mutate(fill = value) %>% 
    select(id, fill) -> df_col
  
  df %>% 
    inner_join(df_col, by='id') %>%
    mutate(source=factor(source, 
                         levels=c("CRO", "JATS", "SEM", 'CRO_ERR', 'SEM_ERR'))) %>% 
    mutate(software_citation_type = ifelse(
      software_citation_type != 'Manual', 'Direct', 'Manual')) -> 
    df_plot
  
  df_plot <- split(df_plot, df_plot$software_citation_type)
  
  alluvial(df_plot$Direct
           , key = source
           , value = value
           , id = id
           , fill = fill
           , order_levels_value = c('M', 'NA', 'US', 'S', 'C', 'E')
           , order_levels_key = c('CRO_ERR', 'CRO', 'JATS', 'SEM', 'SEM_ERR')
           , col_vector_flow = col_vf1
           , col_vector_value = col_v1 
           , stratum_labels = T
           , stratum_label_size = 4.5
           , auto_rotate_xlabs = F
           , labels = labels
           , title = title
           , facet_name = "Direct Software Citation"
  ) -> p_out_1
  
  alluvial(df_plot$Manual
           , key = source
           , value = value
           , id = id
           , fill = fill
           , order_levels_value = c('M', 'NA', 'US', 'S', 'C', 'E')
           , order_levels_key = c('CRO_ERR', 'CRO', 'JATS', 'SEM', 'SEM_ERR')
           , col_vector_flow = col_vf2
           , col_vector_value = col_v2 
           , stratum_label_size = 4.5
           , stratum_labels = T
           , auto_rotate_xlabs = F
           , facet_name = "Citation to Manual", 
  ) -> p_out_2
  
  return(p_out_1 / p_out_2)
}
```

Plotting the results:

```{r, fig.width=11, fig.height=10}
df %>%
  mutate(Version_info = drei(Version, 
                             `Version<>unstructured`, 
                             string='S', 
                             missing=missing)) %>%
  select(source, id, ends_with('_info'), software_citation_type) -> 
  data_long

df %>%
  mutate(Version_info = vier(missing, 
                             Version, 
                             `Version<>wrong_content`, 
                             `Version<>incomplete_content`, 
                             `Version<>wrong_place`)) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  filter(source != 'JATS') %>%
  mutate(source = recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=Version_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,6,5)], 
                     col_vector_flow[c(1,3,2)], 
                     col_vector[c(1,2,3,4,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)", 
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Version representation across databases")

ggsave('db_version.jpg', p, width = 9, height = 5)

p <- p + labs(caption="Fig S6 (Article Fig 10): Adapted alluvial plot illustrating 
        the availability, structure, and correctness of software version 
        representations within Direct Software Citations. The results 
        for availability and structure for the publisher's JATS in the 
        middle column are compared to the results for Crossref (CRO) on 
        the left, Semantic Scholar (SEM) on the right. The outermost 
        columns show the correctness for Crossref (CRO_ERR) on the left 
        and Semantic Scholar on the right (SEM_ERR). Missing samples in 
        Crossref and Semantic Scholar are added in all columns for 
        completeness.")
print(p)

get_main_numbers <- function(df, name){
  df %>% 
    group_by(source, value, software_citation_type) %>% 
    summarize(n=n()) %>% 
    filter(value != 'M') %>%
    group_by(source, software_citation_type) %>%
    mutate(n_total = sum(n)) %>%
    ungroup() %>%
    separate(source, into=c('source', 'error'), '_', fill = "right") %>%
    mutate(error = ifelse(is.na(error), 'none', error)) %>%
    mutate(source = as.character(source)) %>%
    pivot_wider(names_from = value, values_from=n) -> df_tmp
  
  df_tmp <- split(df_tmp, df_tmp$error)
  df_tmp$ERR %>% select(-c(S, US, error)) -> df_tmp_2
  df_tmp$none %>% select(-c(C, E, error)) %>%
    left_join(df_tmp_2, by=c('source', 
                             'software_citation_type', 
                             'n_total', 
                             'NA')) %>%
    mutate(`NA %` = round(`NA` / n_total * 100, 1),
           `S %` = round(`S` / n_total * 100, 1),
           `US %` = round(`US` / n_total * 100, 1),
           `C %` = round(`C` / n_total * 100, 1),
           `E %` = round(`E` / n_total * 100, 1)) %>%
    mutate(`Meta-data` = name) -> df_out
  
  return(df_out)
}

df_table <- get_main_numbers(data_long, "Version")

#cat(software_version(data_long, df))
```

Name:

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(Name_info = drei(Name, 
                          `Name<>unstructured`,
                          string='S', 
                          missing=missing)) %>%
  select(source, id, ends_with('_info'), software_citation_type) -> 
  data_long

df %>%
  mutate(Name_info = vier(missing, 
                          Name, 
                          `Name<>wrong_content`, 
                          `Name<>incomplete_content`, 
                          `Name<>wrong_place`)) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  filter(source != 'JATS') %>%
  mutate(source =  recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=Name_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)", 
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Software name representation across databases")

ggsave('db_name.jpg', p, width = 9, height = 5)

p <- p + labs(caption="Fig S7 (Article Fig 7): Alluvial plot illustrating the 
              availability, structure, and correctness of software name 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)

df_table <- rbind(df_table, get_main_numbers(data_long, "Name"))

#cat(software_name(data_long, df))
```

Year, include information from exact date, date of access and year, in the given priority as they are semantically related and there is only few data on the first two.

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(
    date_info = as.character(drei(PubDate_exact, 
                                  `PubDate_year<>unstructured`, 
                                  string='S', 
                                  missing)),
    doa_info = as.character(drei(Date_of_access, 
                                 `Date_of_access<>unstructured`, 
                                 string='S', 
                                 missing)),
    year_info = as.character(drei(PubDate_year, 
                                  `PubDate_year<>unstructured`, 
                                  string='S', 
                                  missing))) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  mutate(structure_info = ifelse(date_info!='NA', date_info, 
                                  ifelse(doa_info!='NA', doa_info, 
                                         year_info))) %>%
  select(-c(date_info, doa_info, year_info)) -> data_long

df %>%
  mutate(Date_info = as.character(vier(missing, 
                                       PubDate_exact, 
                                       `PubDate_exact<>wrong_content`, 
                                       `PubDate_exact<>incomplete_content`, 
                                       `PubDate_exact<>wrong_place`)),
         DoA_info = as.character(vier(missing, 
                                      Date_of_access, 
                                      `Date_of_access<>wrong_content`, 
                                      `Date_of_access<>incomplete_content`, 
                                      `Date_of_access<>wrong_place`)),
         Year_info = as.character(vier(missing, 
                                       PubDate_year, 
                                       `PubDate_year<>wrong_content`, 
                                       `PubDate_year<>incomplete_content`, 
                                       `PubDate_year<>wrong_place`))) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  mutate(structure_info = ifelse(Date_info!='NA', Date_info, 
                                  ifelse(DoA_info!='NA', DoA_info, 
                                         Year_info))) %>%
  filter(source != 'JATS') %>%
  select(-c(Date_info, DoA_info, Year_info))  %>%
  mutate(source = recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=structure_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     col_vector[c(2,1,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)", 
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Publication date representation across databases")

ggsave('db_year.jpg', p, width = 9, height = 5)

p <- p + labs(caption="Fig S8 (Article Fig 11): Alluvial plot illustrating the 
              availability, structure, and correctness of software release date 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)

df_table <- rbind(df_table, get_main_numbers(data_long, "Date"))

#cat(software_year(data_long, df))
```

Creator:

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(Creator_info = drei(Creator, 
                             `Creator<>unstructured`, 
                             string='S', 
                             missing)) %>%
  select(source, id, ends_with('_info'), software_citation_type) -> 
  data_long

df %>%
  mutate(Creator_info = vier(missing, 
                             Creator, 
                             `Creator<>wrong_content`, 
                             `Creator<>incomplete_content`, 
                             `Creator<>wrong_place`)) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  filter(source != 'JATS') %>%
  mutate(source =  recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=Creator_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     col_vector[c(2,1,4,3,6,5)], 
                     col_vector_flow[c(1,3,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)", 
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Creator representation across databases")

ggsave('db_creator.jpg', p, width = 9, height = 5)

p <- p + labs(caption="Fig S8 (Article Fig 8): Alluvial plot illustrating the 
              availability, structure, and correctness of software release date 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)

df_table <- rbind(df_table, get_main_numbers(data_long, "Developer"))

#cat(software_creator(data_long, df))
```

URL:

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(
    ID_info = as.character(drei(ID, 
                                `ID<>unstructured`,
                                string='S',
                                missing)),
    Archive_info = as.character(drei(Archive, 
                                     `Archive<>unstructured`,
                                     string='S', 
                                     missing)),
    URL_info = as.character(drei(URL, 
                                 `URL<>unstructured`, 
                                 string='S', 
                                 missing))) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  mutate(structure_info = ifelse(ID_info!='NA', ID_info, 
                                  ifelse(Archive_info!='NA', 
                                         Archive_info, 
                                         URL_info))) %>%
  select(-c(ID_info, Archive_info, URL_info)) ->
  data_long

df %>%
  mutate(ID_info = as.character(vier(missing, 
                                     ID, 
                                     `ID<>wrong_content`,
                                     `ID<>incomplete_content`,
                                     `ID<>wrong_place`)),
         Archive_info = as.character(vier(missing, 
                                          Archive, 
                                          `Archive<>wrong_content`, 
                                          `Archive<>incomplete_content`,
                                          `Archive<>wrong_place`)),
         URL_info = as.character(vier(missing,
                                      URL,
                                      `URL<>wrong_content`,
                                      `URL<>incomplete_content`,
                                      `URL<>wrong_place`))) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  mutate(structure_info = ifelse(ID_info!='NA', ID_info, 
                             ifelse(Archive_info!='NA',
                                    Archive_info, 
                                    URL_info))) %>%
  filter(source != 'JATS') %>%
  select(-c(ID_info, Archive_info, URL_info)) %>%
  mutate(source = recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=structure_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,5,6)],
                     col_vector_flow[c(1,3,2)],
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3)],
                     labels=c("not available (NA)",
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)",
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Identifier representation across databases")

ggsave('db_url.jpg', p, width = 9, height = 5)

p <- p + labs(caption="Fig S9 (Article Fig 9): Alluvial plot illustrating the 
              availability, structure, and correctness of software identifier 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)

df_table <- rbind(df_table, get_main_numbers(data_long, "URL"))

#cat(software_identifier(data_long, df))
```

Description:

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(Description_info = drei(Description,
                                 `Description<>unstructured`,
                                 string='S',
                                 missing)) %>%
  select(source, id, ends_with('_info'), software_citation_type) -> 
  data_long

df %>%
  mutate(Description_info = vier(missing, 
                                 Description, 
                                 `Description<>wrong_content`, 
                                 `Description<>incomplete_content`, 
                                 `Description<>wrong_place`)) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  filter(source != 'JATS') %>%
  mutate(source =  recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=Description_info)

p <- create_alluvial(data_long, 
                     col_vector[c(1,2,4,3,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     col_vector[c(1,2,3,4,5,6)], 
                     col_vector_flow[c(1,3,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)",
                              "missing (M)", 
                              "correct (C)",
                              "error (E)", 
                              "unstructured (US)"), 
                     title = "Description representation across databases")

p <- p + labs(caption="Fig S10: Alluvial plot illustrating the 
              availability, structure, and correctness of software description 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)
#ggsave('db_description.jpg', p, width = 9, height = 5)

#cat(software_description(data_long))
```

Type of citation:

```{r, fig.width=11, fig.height=8.5}
df %>% 
  mutate(Type_of_citation_info = drei(Type_of_citation, 
                                      `Type_of_citation<>unstructured`,
                                      string='S',
                                      missing)) %>%
  select(source, id, ends_with('_info'), software_citation_type) -> 
  data_long

df %>%
  mutate(Type_of_citation_info = vier(missing,
                                      Type_of_citation,
                                      `Type_of_citation<>wrong_content`, 
                                      `Type_of_citation<>incomplete_content`,
                                      `Type_of_citation<>wrong_place`)) %>%
  select(source, id, ends_with('_info'), software_citation_type) %>%
  filter(source != 'JATS') %>%
  mutate(source =  recode(source, `CRO`='CRO_ERR', `SEM`='SEM_ERR')) ->
  data_long_2

data_long <- rbind(data_long, data_long_2)
data_long %<>% rename(value=Type_of_citation_info)

p <- create_alluvial(data_long,
                     col_vector[c(1,2,3,4,5,6)],
                     col_vector_flow[c(1,2,3)],
                     col_vector[c(1,2,3,5)],
                     col_vector_flow[c(1,2)], 
                     labels=c("not available (NA)", 
                              "structured (S)", 
                              "missing (M)", 
                              "correct (C)", 
                              "error (E)",
                              "unstructured (US)"),
                     title = "Type of citation representation across databases")

p <- p + labs(caption="Fig S11: Alluvial plot illustrating the 
              availability, structure, and correctness of software type of citation 
              representations within Direct Software Citations following the 
              principle of Figure S6.")
print(p)
#ggsave('db_type.jpg', p, width = 9, height = 5)

#cat(software_type_of_citatin(data_long))
```

Summary table for paper:

```{r}
df_table %>%
  select(`Meta-data`, `software_citation_type`, `source`, `n_total`, `NA`, 
         `NA %`, `US`, `US %`, `S`, `S %`, `C`, `C %`, `E`, `E %`) %>%
  rename(DB=`source`, Citation=`software_citation_type`, n=`n_total`) %>%
  mutate(`Meta-data` = factor(`Meta-data`, levels=c('Name', 'URL', 'Developer',
                                                    'Version', 'Date'))) %>%
  mutate(`DB` = factor(`DB`, levels=c('JATS', 'CRO', 'SEM'))) %>%
  arrange(`Meta-data`, `Citation`, `DB`) -> df_out

#print(xtable(df_out), include.rownames=F)
```

```{r}
sessionInfo()
```
